---
title: "Slideshow Material"
author: "aaron till"
date: "8/10/2018"
output: github_document
---

```{r}
library(ggthemes)
library(sjPlot)
```

Test

```{r}

test <- ggmap(LA_map) +
  geom_point(data=tidy_data, aes(hh_add_lng, hh_add_lat, color = zone), size = 4) +
  geom_point(data = tidy_data, aes(x = denka_lng, denka_lat), shape = 4, size = 3*4)+
  #scale_color_gradient(low = 'grey', high = 'red') +
  guides(color = FALSE, alpha = FALSE) +
    geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21,size = 56*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1,shape = 21, size = 88*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21, size = 134*4, stroke = 2) +
  geom_label(data = cancer_zone_data, aes(x = min_lng - min_lng/30000, y = 30.065, label = zone), size = 8) +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
  
  

test
# convert to 1900 size on monitor or 2100 size on laptop screen, ring 1 should align with road

```

Barplot 0 (numbers in each zone)

```{r}
tidy_data %>%
  group_by(zone) %>%
  summarise(Individuals = n()) %>%
ggplot(aes(x = factor(zone), y = Individuals)) +
  geom_bar(stat = 'identity')+
  xlab('Zone') +
  geom_label(aes(y = 100, label = Individuals)) +
  theme_tufte()

  


```


Map 1 
  Universe: All
  Variable: Cancer

```{r}

map_all_cancer <- ggmap(LA_map) +
  geom_point(data=filter(tidy_data, cancer_aaron == 0), aes(hh_add_lng, hh_add_lat), size = 1*4, fill = 'white', color = 'black', shape = 21) +
  geom_point(data=filter(tidy_data, cancer_aaron  == 1), aes(hh_add_lng, hh_add_lat), size = 1*4, color = 'red') +
  geom_point(data = tidy_data, aes(x = denka_lng, denka_lat), shape = 4, size = 3*4)+
  #scale_color_gradient(low = 'grey', high = 'red') +
  guides(color = FALSE, alpha = FALSE) +
    geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21,size = 56*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1,shape = 21, size = 88*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21, size = 134*4, stroke = 2) +
  geom_label(data = cancer_zone_data, aes(x = min_lng - min_lng/20000, y = 30.065, label = zone), size = 8) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
  
  

map_all_cancer


```

Barplot 1


```{r}

tidy_data %>%
  group_by(zone) %>%
  summarise(cancer_prop = sum(cancer_aaron)/n()) %>%
ggplot(aes(x = factor(zone), y = cancer_prop)) +
  geom_bar(stat = 'identity') +
  ylab('Cancer Proportion') +
  xlab('Zone') +
  geom_label(aes(y = 0.03, label = cancer_prop)) + 
  theme_tufte()


```

Regression Table 1

```{r}

glm_data <- tidy_data %>% 
  select(-cancer) %>%
  mutate('cancer' = cancer_aaron) %>%
  mutate('smoking_hh' = ifelse(real_hh_smoking > 0, 1, 0))

Cancer1 <- glm(cancer ~ denka_dist, data = glm_data, family = 'binomial')


Cancer2 <- glm(cancer ~ denka_dist + age, data = glm_data, family = 'binomial')


Cancer3 <- glm(cancer ~ denka_dist + age + sex, data = glm_data, family = 'binomial')

Cancer4 <- glm(cancer ~ denka_dist + smoking_hh + age + sex, data = glm_data, family = 'binomial')



c1 <- sjt.lm(Cancer1, Cancer2, Cancer3, Cancer4, show.ci = FALSE, show.std = TRUE)

c1


```


Map 2 
  Universe: All
  Variable: Cancer, filter out cancer that occured pre_move in

```{r}

map_cancer_local <- ggmap(LA_map) +
  geom_point(data=filter(tidy_data, cancer_after == 0), aes(hh_add_lng, hh_add_lat), size = 1*4, fill = 'white', color = 'black', shape = 21) +
  geom_point(data=filter(tidy_data, cancer_after  == 1 | is.na(cancer_after)), aes(hh_add_lng, hh_add_lat), size = 1*4, color = 'red') +
  geom_point(data = tidy_data, aes(x = denka_lng, denka_lat), shape = 4, size = 3*4)+
  #scale_color_gradient(low = 'grey', high = 'red') +
  guides(color = FALSE, alpha = FALSE) +
    geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21,size = 56*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1,shape = 21, size = 88*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21, size = 134*4, stroke = 2) +
  geom_label(data = cancer_zone_data, aes(x = min_lng - min_lng/20000, y = 30.065, label = zone), size = 8) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
  
  

map_cancer_local

```

Barplot 2


```{r}

tidy_data %>%
  mutate(cancer_after = ifelse(is.na(cancer_after),1, cancer_after)) %>%
  group_by(zone) %>%
  summarise(cancer_prop = sum(cancer_after)/n()) %>%
ggplot(aes(x = factor(zone), y = cancer_prop)) +
  geom_bar(stat = 'identity') +
  ylab('Cancer Proportion') +
  xlab('Zone') +
  geom_label(aes(y = 0.03, label = cancer_prop)) + 
  theme_tufte()


```

Regression Table 2

```{r}

glm_data <- tidy_data %>% 
  select(-cancer) %>%
  mutate('cancer' = cancer_aaron) %>%
  mutate('smoking_hh' = ifelse(real_hh_smoking > 0, 1, 0)) %>%
  mutate('cancer_filtered' = ifelse(is.na(cancer_after),1, cancer_after))

Cancer1 <- glm(cancer_filtered ~ denka_dist, data = glm_data, family = 'binomial')


Cancer2 <- glm(cancer_filtered ~ denka_dist + age, data = glm_data, family = 'binomial')


Cancer3 <- glm(cancer_filtered ~ denka_dist + age + sex, data = glm_data, family = 'binomial')

Cancer4 <- glm(cancer_filtered ~ denka_dist + smoking_hh + age + sex, data = glm_data, family = 'binomial')



c2 <- sjt.lm(Cancer1, Cancer2, Cancer3, Cancer4, show.ci = FALSE, show.std = TRUE)

c2


```




Map 3 
  Universe: Respondents
  Variable: Cancer after move in

```{r}

map_respondents_cancer_local <- ggmap(LA_map) +
  geom_point(data=filter(tidy_data, cancer_after == 0 & respondent == 1), aes(hh_add_lng, hh_add_lat), size = 1*4, fill = 'white', color = 'black', shape = 21) +
  geom_point(data=filter(tidy_data, cancer_after  == 1 & respondent == 1), aes(hh_add_lng, hh_add_lat), size = 1*4, color = 'red') +
  geom_point(data = tidy_data, aes(x = denka_lng, denka_lat), shape = 4, size = 3*4)+
  #scale_color_gradient(low = 'grey', high = 'red') +
  guides(color = FALSE, alpha = FALSE) +
    geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21,size = 56*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1,shape = 21, size = 88*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21, size = 134*4, stroke = 2) +
  geom_label(data = cancer_zone_data, aes(x = min_lng - min_lng/20000, y = 30.065, label = zone), size = 8) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
  
  

map_respondents_cancer_local

```

Barplot 3


```{r}

tidy_data %>%
  filter(respondent == 1) %>%
  group_by(zone) %>%
  summarise(cancer_prop = sum(cancer_after)/n()) %>%
ggplot(aes(x = factor(zone), y = cancer_prop)) +
  geom_bar(stat = 'identity') +
  ylab('Cancer Proportion') +
  xlab('Zone') +
  geom_label(aes(y = 0.03, label = cancer_prop)) + 
  theme_tufte()


```

Regression Table 3

```{r}

glm_data <- tidy_data %>% 
  filter(respondent == 1) %>%
  select(-cancer) %>%
  mutate('cancer' = cancer_aaron) %>%
  mutate('smoking_hh' = ifelse(real_hh_smoking > 0, 1, 0)) %>%
  mutate('cancer_filtered' = ifelse(is.na(cancer_after),1, cancer_after))

Cancer1 <- glm(cancer_after ~ denka_dist, data = glm_data, family = 'binomial')


Cancer2 <- glm(cancer_after ~ denka_dist + age, data = glm_data, family = 'binomial')


Cancer3 <- glm(cancer_after~ denka_dist + age + sex, data = glm_data, family = 'binomial')

Cancer4 <- glm(cancer_after ~ denka_dist + smoking_hh + age + sex, data = glm_data, family = 'binomial')



c3 <- sjt.lm(Cancer1, Cancer2, Cancer3, Cancer4, show.ci = FALSE, show.std = TRUE)

c3


```


Maps 4 
  Universe: Respondents
  Variable: Cancer after move in, or cancer after move in to select previous residence

```{r}

 # var = cancer_after_cities

map_respondents_cancer_wider <- ggmap(LA_map) +
  geom_point(data=filter(tidy_data, cancer_after_cities == 0 & respondent == 1), aes(hh_add_lng, hh_add_lat), size = 1*4, fill = 'white', color = 'black', shape = 21) +
  geom_point(data=filter(tidy_data, cancer_after_cities  == 1 & respondent == 1), aes(hh_add_lng, hh_add_lat), size = 1*4, color = 'red') +
  geom_point(data = tidy_data, aes(x = denka_lng, denka_lat), shape = 4, size = 3*4)+
  #scale_color_gradient(low = 'grey', high = 'red') +
  guides(color = FALSE, alpha = FALSE) +
    geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21,size = 56*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1,shape = 21, size = 88*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21, size = 134*4, stroke = 2) +
  geom_label(data = cancer_zone_data, aes(x = min_lng - min_lng/20000, y = 30.065, label = zone), size = 8) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
  
  

map_respondents_cancer_wider

```

Barplot 4


```{r}

tidy_data %>%
  filter(respondent == 1) %>%
  group_by(zone) %>%
  summarise(cancer_prop = sum(cancer_after_cities)/n()) %>%
ggplot(aes(x = factor(zone), y = cancer_prop)) +
  geom_bar(stat = 'identity') +
  ylab('Cancer Proportion') +
  xlab('Zone') +
  geom_label(aes(y = 0.03, label = cancer_prop)) + 
  theme_tufte()


```

Regression Table 4

```{r}

glm_data <- tidy_data %>% 
  filter(respondent == 1) %>%
  select(-cancer) %>%
  mutate('cancer' = cancer_aaron) %>%
  mutate('smoking_hh' = ifelse(real_hh_smoking > 0, 1, 0)) %>%
  mutate('cancer_filtered' = ifelse(is.na(cancer_after),1, cancer_after))

Cancer1 <- glm(cancer_after_cities ~ denka_dist, data = glm_data, family = 'binomial')


Cancer2 <- glm(cancer_after_cities ~ denka_dist + age, data = glm_data, family = 'binomial')


Cancer3 <- glm(cancer_after_cities~ denka_dist + age + sex, data = glm_data, family = 'binomial')

Cancer4 <- glm(cancer_after_cities ~ denka_dist + smoking_hh + age + sex, data = glm_data, family = 'binomial')



c4 <- sjt.lm(Cancer1, Cancer2, Cancer3, Cancer4, show.ci = FALSE, show.std = TRUE)

c4


```


Map 5
  Universe: All respondents moved in after 2013
  Variable: Cancer after move in


```{r}

map_respondents_cancer_2013 <- ggmap(LA_map) +
  geom_point(data=filter(tidy_data, cancer_after == 0 & move_in_year <= 2013), aes(hh_add_lng, hh_add_lat), size = 1*4, fill = 'white', color = 'black', shape = 21) +
  geom_point(data=filter(tidy_data, cancer_after  == 1 & move_in_year <= 2013), aes(hh_add_lng, hh_add_lat), size = 1*4, color = 'red') +
  geom_point(data = tidy_data, aes(x = denka_lng, denka_lat), shape = 4, size = 3*4)+
  #scale_color_gradient(low = 'grey', high = 'red') +
  guides(color = FALSE, alpha = FALSE) +
    geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21,size = 56*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1,shape = 21, size = 88*4, stroke = 2)+
  geom_point(data = tidy_data[0:1,], aes(denka_lng, denka_lat), alpha = 1, shape = 21, size = 134*4, stroke = 2) +
  geom_label(data = cancer_zone_data, aes(x = min_lng - min_lng/20000, y = 30.065, label = zone), size = 8) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
  
  

map_respondents_cancer_2013

```

Barplot 5

```{r}

tidy_data %>%
  filter(move_in_year <= 2013) %>%
  group_by(zone) %>%
  summarise(cancer_prop = sum(cancer_after)/n()) %>%
ggplot(aes(x = factor(zone), y = cancer_prop)) +
  geom_bar(stat = 'identity') +
  ylab('Cancer Proportion') +
  xlab('Zone') +
  geom_label(aes(y = 0.03, label = cancer_prop)) + 
  theme_tufte()


```

Regression Table 4

```{r}

glm_data <- tidy_data %>% 
  filter(cancer<=2013) %>%
  select(-cancer) %>%
  mutate('cancer' = cancer_aaron) %>%
  mutate('smoking_hh' = ifelse(real_hh_smoking > 0, 1, 0)) %>%
  mutate('cancer_filtered' = ifelse(is.na(cancer_after),1, cancer_after))

Cancer1 <- glm(cancer_after ~ denka_dist, data = glm_data, family = 'binomial')


Cancer2 <- glm(cancer_after ~ denka_dist + age, data = glm_data, family = 'binomial')


Cancer3 <- glm(cancer_after ~ denka_dist + age + sex, data = glm_data, family = 'binomial')

Cancer4 <- glm(cancer_after~ denka_dist + smoking_hh + age + sex, data = glm_data, family = 'binomial')



c5 <- sjt.lm(Cancer1, Cancer2, Cancer3, Cancer4, show.ci = FALSE, show.std = TRUE)

c5


```

Barplot 6
  Length of current residence by zone

```{r}

tidy_data %>%
  filter(!is.na(move_in_year)) %>%
  group_by(zone) %>%
  summarise(length = median(2018 - move_in_year)) %>%
ggplot(aes(x = factor(zone), y = length)) +
  geom_bar(stat = 'identity') +
  ylab('Median Years of Residence') +
  xlab('Zone') +
  geom_label(aes(y = 10, label = length)) + 
  theme_tufte()


```



Barplot 7
  Length of cancer by zone

```{r}

tidy_data %>%
  filter(cancer_year>0) %>%
  group_by(zone) %>%
  summarise(length = median(2018 - cancer_year)) %>%
ggplot(aes(x = factor(zone), y = length)) +
  geom_bar(stat = 'identity') +
  ylab('Median Years of Cancer') +
  xlab('Zone') +
  geom_label(aes(y = 2, label = length)) + 
  theme_tufte()


```
Barplot 8
  Years of residence before cancer

```{r}

tidy_data %>%
  filter(cancer_year>0 & !is.na(move_in_year)) %>%
  group_by(zone) %>%
  summarise(length = median(cancer_year - move_in_year)) %>%
ggplot(aes(x = factor(zone), y = length)) +
  geom_bar(stat = 'identity') +
  ylab('Median Years of Residence Before Cancer') +
  xlab('Zone') +
  geom_label(aes(y = 10, label = length)) + 
  theme_tufte()


```


Barplot 9
  Median age of developing cancer

```{r}

tidy_data %>%
  filter(cancer_year>0) %>%
  group_by(zone) %>%
  summarise(length = median(age - (2018-cancer_year))) %>%
ggplot(aes(x = factor(zone), y = length)) +
  geom_bar(stat = 'identity') +
  ylab('Median Age of Cancer Diagnosis') +
  xlab('Zone') +
  geom_label(aes(y = 10, label = length)) + 
  theme_tufte()


```



Barplot 10
  Median age of cancer death
  
  
```{r}

incomplete_age_cancer_death_data %>%
  group_by(zone) %>%
  summarise(length = median(age)) %>%
ggplot(aes(x = factor(zone), y = length)) +
  geom_bar(stat = 'identity') +
  ylab('Median Age of Primary Cancer Death per Household') +
  xlab('Zone') +
  geom_label(aes(y = 10, label = length)) + 
  theme_tufte()


```


Barplot 11
  Respiratory complication rates
  
  
```{r}

tidy_data %>%
  mutate(asthma = ifelse(asthma_year > 0 & !is.na(asthma_year), 1, 0), bronchitis = ifelse(bronchitis_year > 0 & !is.na(bronchitis_year), 1, 0), sinus = ifelse(sinus_year > 0 & !is.na(sinus_year), 1, 0))%>%
  group_by(zone) %>%
  summarise(asthma = sum(asthma), Asthma = asthma/n(), bronchitis = sum(bronchitis), Bronchitis = bronchitis/n(), sinus = sum(sinus), Sinus = sinus/n()) %>%
  gather('Type', 'Proportion', Asthma, Bronchitis, Sinus) %>%
ggplot(aes(x = Type, y = Proportion))  +
  geom_bar(stat = 'identity') +
  facet_grid(.~factor(zone)) + 
  ylab('Proportion Suffering from Respiratory Illness') +
  xlab('Zone') +
  geom_label(aes(y = 0.05, label = round(Proportion, 3))) + 
  theme_tufte()


```


Barplot 12
  Childhood Ailments
  
  
```{r}

tidy_data %>%
  filter(age < 12) %>%
  filter(grepl('([A-Z]{5}|[:alnum:]{0,3})\\sWard', school_name) | grepl('E([^\\s]{0,1}|ast)\\sS[^\\s]{1,4}\\sJ', school_name)) %>%
  mutate(nosebleeds = ifelse(nosebleeds == 1 & !is.na(nosebleeds), 1, 0), headaches = ifelse(headaches == 1  & !is.na(headaches), 1, 0)) %>%
  group_by(zone) %>%
  summarise(nosebleeds = sum(nosebleeds), Nosebleeds = nosebleeds/n(), headaches = sum(headaches), Headaches = headaches/n(), n()) %>%
  gather('Type', 'Proportion', Nosebleeds, Headaches) %>%
ggplot(aes(x = Type, y = Proportion))  +
  geom_bar(stat = 'identity') +
  facet_grid(.~factor(zone)) + 
  ylab('Proportion Children With Nosebleeds and Headaches') +
  xlab('Zone') +
  geom_label(aes(y = 0.05, label = round(Proportion, 3))) + 
  theme_tufte()


```


